FTLR proof cases

### 2018-06-12 fully-abstract-comp/ftlr-proof-cases.tex
Small text update

Case \ref{case:ftlr:scall:reg}, using assumption $\npair[n'-1]{(\reg_S\update{r}{z},\reg_T\update{r}{z})} \in \lrr(W_R)$, we get a way to split the ownership of $W_R$.
We take this as the starting point, but with the following changes: regions $r_1$ and $r_2$ maps to worlds with no ownership.
region $\rstk$ maps to a world with the same ownership, but of course without the now revoked regions.
Region $\rretd$ maps to a world that owns private $r_\var{priv\_stk}$ region.
Finally, $\rretc$ maps to a world with the ownership of $W$.

>>>>

Case \ref{case:ftlr:scall:reg}: We need to split the ownership of $W_R'$.
From assumption $\npair[n'-1]{(\reg_S\update{r}{z},\reg_T\update{r}{z})} \in \lrr(W_R)$, we get a way to split the ownership of $W_R$.
We take this as the starting point, but with the following changes: regions $r_1$ and $r_2$ maps to worlds with no ownership (i.e.\ $\purePart{W_{R,1}'}$).
region $\rstk$ maps to a world with the same ownership, but of course without the now revoked regions.
Region $\rretd$ maps to a world that owns private $r_\var{priv\_stk}$ region.
Finally, $\rretc$ maps to a world with the ownership of $W$.
